### 2023-02-01 manuscript.tex
more references [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/66cf80eb0cdc5217862aa9b9080e957b1073a1f9.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/66cf80eb0cdc5217862aa9b9080e957b1073a1f9/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4067158862

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/5c660e0d407c65b4f669383e77cc59e770e73c12/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/5c660e0d407c65b4f669383e77cc59e770e73c12}{stain/2022-fdo-paper@5c660e0}
on February 1, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/66cf80eb0cdc5217862aa9b9080e957b1073a1f9/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/66cf80eb0cdc5217862aa9b9080e957b1073a1f9}{stain/2022-fdo-paper@66cf80e}
on February 1, 2023.
